Robotic Cart System

### 2021-04-13 parts/30-customized_parabolic_reflector_array.tex
Cleared out empty sections of final report
Update 30-customized_parabolic_reflector_array.tex

%----------------------------------------------------------------------
\section{Reflector Design}
%----------------------------------------------------------------------
The XBee RF modules that were used detect signals from any direction. For this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming. To accomplish this, two different models of reflector arrays were designed and constructed.

\subsection{Purely Paraboloidal Reflector}
The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a purely paraboloidal shape. This shape was selected since all signals entering the reflector parallel to the axis of the reflector will pass through the focus of the paraboloid. By mounting the XBee such that the center of the antenna coincides with the focus of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
\begin{figure}
    \centering
    \includegraphics[width=3.5in]{figs/img/paraboloidalReflector.png}
    \caption{Purely Paraboloidal Reflector Array}
    \label{fig:paraboloidalReflector}
\end{figure}

@@

%----------------------------------------------------------------------
\section{Experimental Results}
%----------------------------------------------------------------------

>>>>

%----------------------------------------------------------------------
\section{Reflector Design}
%----------------------------------------------------------------------
The XBee RF modules that were used detect signals from any direction. In this project, however, it is desired to have differences in the received signals based on the angle from which the signal is coming. To accomplish this, two different models of reflector arrays were designed and constructed.

\subsection{Paraboloidal Reflector}
The first design, shown in \autoref{fig:paraboloidalReflector}, uses a reflector with a paraboloidal shape. This shape was selected since all signals entering the reflector parallel to the axis of the reflector will be focused at the focal point of the paraboloid. By mounting the XBee such that the center of the antenna coincides with the focal point of the paraboloid, the signal strength of the signals entering parallel to the axis will be maximized.
\begin{figure}
    \centering
    \includegraphics[width=3.5in]{figs/img/paraboloidalReflector.png}
    \caption{Purely Paraboloidal Reflector Array}
    \label{fig:paraboloidalReflector}
\end{figure}

@@
